Comprehensive Comparison of Deep Learning Models for Lung and COVID-19 Lesion Segmentation in CT scans

### 2021-02-03 ms.tex
fix email

\address[1]{Visual Computing Lab of the Information Technologies Institute, Centre for Research and Technology Hellas, Thessaloniki, Greece e-mail: \{pbizopoulos,vretos,daras\}@iti.gr}

>>>>

\address[1]{Visual Computing Lab of the Information Technologies Institute, Centre for Research and Technology Hellas, Thessaloniki, Greece e-mail: pbizopoulos@protonmail.com,\{vretos,daras\}@iti.gr}
